The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-10-02 beamer/dit-paper-presentation.tex
I hadn't done a COMMIT in some time so here it is

@@

	\begin{frame}{Model}
  \begin{block}{Definition}
  Systems with real-time constraints. (e.g. ABS, VOD, etc)
  \end{block}
  \textbf{Model:} Set of tasks $\tau_i = (O_i, T_i, D_i, C_i)$ generating jobs $J_{i,j}$, with
      \begin{itemize}
      \item $O_i$ : arrival of the first job
      \item $T_i$ : time between two jobs
      \item $D_i$ : relative deadline
      \item $C_i$ : execution time
    \end{itemize}

@@

	\begin{frame}{Feasibility}
		We define feasibility...
	\end{frame}

	\begin{frame}{DBF test}
		\begin{block}{Definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{block}

		Mathematically,
		\[
			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
		\]
		where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
		and deadlines are both in the closed interval $[t_1, t_2]$.

		The values of the $n_i$ are given by \cite{baruah1999generalized}

		CNS of feasibility: $\dbf{t1, t2} \leqslant t2 - t1$
	\end{frame}

	\subsection{Related works}

    \subsubsection{The C-space}

@@

        A region of $\mathbb{N}_0^n$ such as the C-space can be described by a list of parametric linear constraints (called the \emph{formulation}), such as those given by the DBF test.
    \end{frame}

    \begin{frame}{Removing Redundancies in the C-space of synchronous system}

@@

	Extension of the previous results

@@

	\begin{frame}{Definition of the FPDIT}
		We define the following notions, which do not depend on the WCET values:
		\begin{block}{Definition}
			A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
			released strictly before instant $t$ has its absolute deadline before or at instant $t$.
		\end{block}
		\begin{block}{Definition}
			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{block}

@@

	\subsection{Existence and value}

	\begin{frame}{Existence and value}
		The FPDIT is a time $t_d$ for which
		\[
			\begin{array}{l}
				\forall i \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]

		Note that in the synchronous case $t_d = H$ is always a solution ($a_i = T_i$)
	\end{frame}

@@

>>>>

\begin{frame}
    \tableofcontents[currentsection]
\end{frame}

@@

	\begin{frame}{Model}
  \begin{block}{Definition}
  Systems with real-time constraints. (e.g. ABS, VOD, etc)
  \end{block}
  \textbf{Model:} Set of tasks $\tau_i = (O_i, T_i, D_i, C_i)$ generating jobs $J_{i,j}$, with
      \begin{itemize}
      \item $O_i$ : arrival of the first job
      \item $T_i$ : time between two job arrivals
      \item $D_i$ : relative deadline
      \item $C_i$ : execution time
    \end{itemize}

@@

    \subsection{Feasibility}

	\begin{frame}{Feasibility}
		\begin{block}{Feasibility}
        A task set is said to be \textbf{feasible} if there exists a schedule such that every job in the task set completes before its deadline is reached.
        \end{block}

        \begin{block}{Feasibility}
        A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
        \end{block}

        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is EDF-schedulable.
	\end{frame}

    \subsection{C-space}

@@

        \begin{itemize}
            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints
            \item An efficient description allows us to quickly  whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
        \end{itemize}

	\section{Related works}

\begin{frame}
    \tableofcontents[currentsection]
\end{frame}

    \subsection{Demand-bound function}

    \begin{frame}{Demand-bound function feasibility test}
        \begin{block}{Definition}
            The \textbf{demand-bound function (DBF)}
            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
            the maximal cumulated execution time of jobs of $\tau$ contained in the
            closed interval $[t_1, t_2]$.
        \end{block}
        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
        where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
        and deadlines are both in the closed interval $[t_1, t_2]$.

        ~\\

        The following has been shown to be a necessary and sufficient condition of feasibility (called DBF test in the following): $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$

    \subsection{C-space of synchronous systems}

    \begin{frame}{Description using the DBF test}
    The DBF test gives us a set of constraints
    $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$

    \begin{itemize}
        \item Every constraint is linear in the $C_i$ values
        \item Every constraint is necessary
        \item Their conjunction is sufficient
        \pause
        \item But we have an infinite number of constraints!
        \item $\Rightarrow$ Removing redundancy
    \end{itemize}
    \end{frame}

    \begin{frame}{Removing redundancy for synchronous system}

    The authors of \cite{george2009characterization} obtain an efficient description of the C-space by
    \begin{itemize}
        \item Removing constraints in which $t_1 > 0$
        \item Removing constraints in which $t_2$ is not a deadline or $t_2 > H$ (where $H = LCM(T_i)$)
    \end{itemize}

    ~\\
    \pause

    They also define the notion of \textbf{definitive idle times (DIT)} and show that the first one happens at a time $0 < t_d \leqslant H$. Finally they show that all constraints where $t_2 > t_d$ are also redundant.

    ~\\
    \pause

    The remaining constraints are thus the DBF test on intervals $[0, t]$, where $t$ is a deadline and $0 < t \leqslant t_d$. The remaining redundancies are removed by an algorithm based on the simplex.

@@

	In this paper, we
    \begin{itemize}
        \item Introduce the notion of \textbf{first periodic DIT (FPDIT)} as a generalization of the notion of DIT
        \item Provide an algorithm to find an efficient description of the C-space for any periodic system
        \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
    \end{itemize}

@@

	\begin{frame}{Definition of the FPDIT}
		\begin{block}{Definition}
			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{block}

        The FPDIT is the smallest $t_d$ such as:
       \begin{equation}
            \begin{array}{l}
                \forall \tau_i \in \tau, \exists a_i \in [D_i,T_i] \; :\\
                \left\{
                    \begin{array}{l}
                        t_d > O_i \\
                        t_d - O_i \equiv a_i \; (mod \; T_i)
                        \\
                    \end{array}
                \right.
            \end{array}
            \label{eq:FPDIT}
        \end{equation}

        For given values of $a_i$, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]

@@

	\subsection{Finding the FPDIT value}

	\begin{frame}{Existence and value}

@@

\bibliographystyle{IEEEtran}
\bibliography{dit-paper}

### 2013-10-02 dit-paper_ieee.tex
I hadn't done a COMMIT in some time so here it is

		Mathematically,
		\begin{equation}
			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
		\end{equation}
		where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ which arrival times
		and deadlines are both in the closed interval $[t_1, t_2]$.

>>>>

		Mathematically,
		\begin{equation}
			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
		\end{equation}
		where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
		and deadlines are both in the closed interval $[t_1, t_2]$.
